### 2017-10-22 TechnicalReport/article_3.tex
Update article_3.tex
Added algorithm we used

@@

>>>>

El diseño del algoritmo Jaccard que usamos fue el siguiente:

"
Function dist_JaccardSimilarity (InputMatrix : t2dVariantArrayDouble; aZeroThresh: Double; Var OutputMatrix : t2dVariantArrayDouble) : Boolean;
// The function dist_JaccardSimilarity calculates the Jaccard similarity between
// several cases based on binary values (e.g. presences/absences or TRUE/FALSE).
// The variable aZeroThresh defines the minumum value, that is required to
// interpret a variable as being logically TRUE.
// The cases are expected in the rows. The variables are expected
// in the columns. Function returns FALSE if at least one cell can not be
// calculated. The result matrix is returned in OutputMatrix.
// (c) Dr. Jan Schulz, 05.May 2008; www.code10.info
Var  OutputMatrixSize : Integer;
     InputCols        : Integer;
     InputRows        : Integer;
     RunnerY          : Integer;
     RunnerX          : Integer;
     J01              : Integer;
     J10              : Integer;
     J11              : Integer;
     i                : Integer;
     Denominator      : Integer;
     Quotient         : Double;
     FirstVal         : Boolean;
     SecondVal        : Boolean;
Begin
  // if one dimension is zero or matrix not rectangular
  If Not mtx_IsRectangular (InputMatrix, InputRows, InputCols) THen
  Begin
    //create an empty matrix, return FALSE and exit
    mtx_Create (OutputMatrix, 1, 1, 0, 'Erroneous Jaccard similarity matrix');
    dist_JaccardSimilarity := False;
    Exit;
  end;

  // Threshold for binary level needs to be positive
  aZeroThresh := Abs (aZeroThresh);

  // let's expect the best case ...
  dist_JaccardSimilarity := True;

  // define and set the row dimension of the result matrix
  OutputMatrixSize := High (InputMatrix.Cells) + 1;
  SetLength (OutputMatrix.Cells, OutputMatrixSize);

  // create the column dimension of the array
  For RunnerY := Low (OutputMatrix.Cells) to High (Outputmatrix.Cells) do
  Begin
    SetLength (OutputMatrix.Cells [RunnerY], OutputMatrixSize);
  end;

  // define title of matrix
  OutputMatrix.MatrixName := 'Jaccard similarity matrix';

   // Set Row/Col-Title for the new matrix
  SetLength (OutputMatrix.RowTitle, OutputMatrixSize);
  SetLength (OutPutMatrix.ColTitle, OutPutMatrixSize);

  For RunnerY := Low (InputMatrix.RowTitle) to High (InputMatrix.RowTitle) do
  Begin
    // names for rows and columns are the same in this triangualary matrix
    OutputMatrix.RowTitle [RunnerY] := InputMatrix.RowTitle [RunnerY];
    OutputMatrix.ColTitle [RunnerY] := InputMatrix.RowTitle [RunnerY];
  end;

  // compare every object
  For RunnerY := Low (OutputMatrix.Cells) to High (OutputMatrix.Cells) do
  Begin
    //with every other object
    For RunnerX := Low (OutputMatrix.Cells) to RunnerY do
    Begin
      J01 := 0;
      J10 := 0;
      J11 := 0;

      //include all variables in analysis
      For i := 0 to High (InputMatrix.Cells [0]) do
      Begin
        // directly convert to binary variables
        FirstVal  := Abs (InputMatrix.Cells [RunnerX, i]) > aZeroThresh;
        SecondVal := Abs (InputMatrix.Cells [RunnerY, i]) > aZeroThresh;

        If FirstVal And SecondVal THen
        Begin
          J11 := J11 + 1;
        end
        Else
        Begin
          If FirstVal Then J10 := J10 + 1;
          If SecondVal Then J01 := J01 + 1;
        end;
      end;

      Denominator := J01 + J10 + J11;
      If Denominator > 0 THen Quotient := J11 / Denominator
                         Else
                         Begin
                           Quotient := NaN;
                           dist_JaccardSimilarity := False;
                         end;

      // set the calculated value on both sides of diagonal and diagonal itself
      OutputMatrix.Cells [RunnerX, RunnerY] := Quotient;
      OutputMatrix.Cells [RunnerY, RunnerX] := Quotient;
    end;
  end;
end;

Function dist_JaccardDissimilarity (InputMatrix : t2dVariantArrayDouble; aZeroThresh: Double; Var OutputMatrix : t2dVariantArrayDouble) : Boolean;
// The function dist_JaccardDissimilarity calculates the Jaccard dissimilarity
// matrix between several cases, which are expected in the rows. The variables are
// expected in the columns. Function returns FALSE if at least one cell can not be
// calculated. The result matrix is returned in OutputMatrix. This function depends
// on the function CalcCanberraDissimilarityMatrix
// (c) Dr. Jan Schulz, 05.May 2008; www.code10.info
Var RunnerX : Integer;
    RunnerY : Integer;
Begin
  // calculate the Canberra Dissimilarity matrix
  Result := dist_JaccardSimilarity (InputMatrix, aZeroThresh, OutputMatrix);

  // convert the similarity into a dissimilarity matrix
  For RunnerY := Low (OutputMatrix.Cells) to High (OutputMatrix.Cells) do
  Begin
    For RunnerX := Low (OutputMatrix.Cells [RunnerY]) to High (OutputMatrix.Cells [RunnerY]) do
    Begin
      OutPutMatrix.Cells [RunnerY, RunnerX] := 1 - OutPutMatrix.Cells [RunnerY, RunnerX];
    end;
  end;

  If Result THen OutputMatrix.MatrixName := 'Jaccard dissimilarity matrix'
            Else OutputMatrix.MatrixName := 'Erroneous Jaccard dissimilarity matrix';
end;
" \cite{jaccard_seudo}.

@@

\begin{thebibliography}{9}

\bibitem{jaccard_seudo}
Schulz, D. (2017). Jaccard similarity. [online] Code10.info. Available at: \\\texttt{http://www.code10.info/index.php?option=com_content&view=article&id=60:articlejaccard-similarity&catid=38:cat_coding_algorithms_data-similarity&Itemid=57} [Accessed 22 Oct. 2017].
\end{thebibliography}
